Implications of Differential Evolution for Defect Prediction: Analytics Without Parameter Tuning Considered Harmful?

### 2015-03-10 dm101.tex
Updates from ShareLaTeX

Software assessment budgets are finite
while assessment effectiveness increases 
exponentially with assessment effort.
Lowry et al. warn that  
the state space explosion problem imposes
strict limits on how much a system can be explored
via automatic formal methods~\cite{lowrey98}.
For standard black-box testing methods,
a {\em linear} increase
in the confidence $C$ that we have found all defects
can take {\em exponentially} more effort.
For example, for one-in-a-thousand detects,
moving $C$ from  
90\% to 94\% to 98\% takes 2301, 2812, and 3910 black box
probes, respectively.\footnote{A randomly selected 
input to a program will find a fault with probability $p$.
After $N$ random black-box tests, the chances of the inputs 
not revealing any fault 
is $(1-p)^N$. Hence, the chances $C$ of seeing the fault is $1-(1-p)^N$
which can be rearranged to 
 $N(C,p)=\frac{log(1 -
C)}{log(1-p)}$. For example, $N(0.90,10^{-3})=2301$.}

@@

There are many reasons to study defect  defect predictors learned from
static code attributes: they are   {\em easy to
use}, {\em widely-used}, and {\em useful} to use.

{\em Easy to use:} Static code attributes can be automatically and cheaply collected, even for very large systems~\cite{nagappan05}.
By contrast, 
other methods such as manual code reviews are labor-intensive.
Depending on the review methods 8 to 20 LOC/minute can be
inspected and this effort repeats for all members of the review team,
which can be as large as four or six~\cite{me02f}.

@@

{\em Useful:}
A
standard result for defect predictors is that they find the location of  70\% (or more)
of the defects in code.
This is markedly
higher than other currently-used
industrial
methods such as manual code reviews:
\bi
\item
A panel at {\em IEEE Metrics
2002}~\cite{shu02} concluded that manual software  reviews can find ${\approx}60\%$ 
of defects.
\item
Raffo found that the defect detection capability of
industrial review methods have mode defect detection rates
of around 50\%
 for full Fagan inspections~\cite{fagan76} to
21\% for less-structured inspections.
\ei
Defect prediction scales well to a commercial
context. Defect predicting technology has been
commercialized in {\it Predictive}~\cite{turner06} a
%scalable product suite to analyze and predict
defects in software projects. Predictive was observed to
highlight simimilar issues to those found   with the more expensive tools. But,
Predictive was able to faster process a larger code
base than the more expensive tool~\cite{turner06}.

In addition, defect predictors developed at NASA~\cite{me07b} have also been used in software development companies outside the US (in Turkey). When the inspection teams focused on the modules that trigger the defect predictors, they found up to 70\% of the defects using just 40\% of their QA effort (measured in staff hours)~\cite{tosun10}.

Finally, a subsequent study on the Turkish software
compared how much code needs to be inspected using
random selection vs. selection via defect
predictors. Using random testing, 87\% of the files
would have to be inspected in order to detect 87\%
of the defects. However, if the inspection process
was restricted to the 25\% of the files that trigger
the defect predictors, then 88\% of the defects
could be found. That is, the same level of defect
detection (after inspection) can be achieved using
$(87-25)/87=71$\%less effort
\cite{tosun09}.

>>>>

Human programmers are clever, but flawed. Coding  adds functionality, but also defects.
Hence, software sometimes crashes (perhaps at the most awkward or dangerous moment) or delivers
the wrong functionality. For a very long list of software-related errors,
see  Peter Neumann's ``Risk Digest''\footnote{http://catless.ncl.ac.uk/Risks/}.

Because of the above, is important to thoroughly {\em test} software before it is {\em used}.
Such testing  can be very expensive.
Software assessment budgets are finite
while assessment effectiveness increases 
exponentially with assessment effort.
Lowry et al. warn that  
the state space explosion problem imposes
strict limits on how much a system can be explored
via automatic formal methods~\cite{lowrey98}.
For standard black-box testing methods,
a {\em linear} increase
in the confidence $C$ that we have found all defects
can take {\em exponentially} more effort.
For example, for one-in-a-thousand detects,
moving $C$ from  
90\% to 98\% nearly doubles the number of required tests (2301 to   3910 black box
probes, respectively)\footnote{A randomly selected 
input to a program will find a fault with probability $p$.
After $N$ random black-box tests, the chances of the inputs 
not revealing any fault 
is $(1-p)^N$. Hence, the chances $C$ of seeing the fault is $1-(1-p)^N$
which can be rearranged to 
 $N(C,p)=\frac{log(1 -
C)}{log(1-p)}$. For example, $N(0.90,10^{-3})=2301$.}.

@@

One such lightweight sampling policy is defect predictors learned from static code attributes.
Given software described using (for example) the attributes of \fig{ck} it is possible
to use standard data mining technology to learn where the probability of software defects is highest.
Such defect  defect predictors learned from
static code attributes are   {\em easy to
use}, {\em widely-used}, and {\em useful} to use.

{\em Easy to use:} Static code attributes can be automatically collected, even for very large systems~\cite{nagappan05}.
Other methods, like  manual code reviews, are far slower and far more labor-intensive.
For example, depending on the review methods 8 to 20 LOC/minute can be
inspected and this effort repeats for all members of the review team,
which can be as large as four or six~\cite{me02f}.

@@

{\em Useful:}
A
standard result for defect predictors is that they find the location of  70\% (or more)
of the defects in code~\cite{me70b}.
Defect predictors developed at NASA~\cite{me07b} have also been used in software development companies outside the US (in Turkey). When the inspection teams focused on the modules that trigger the defect predictors, they found up to 70\% of the defects using just 40\% of their QA effort (measured in staff hours)~\cite{tosun10}.
A subsequent study on the Turkish software
compared how much code needs to be inspected using
random selection vs. selection via defect
predictors. Using random testing, 87\% of the files
would have to be inspected in order to detect 87\%
of the defects. However, if the inspection process
was restricted to the 25\% of the files that trigger
the defect predictors, then 88\% of the defects
could be found. That is, the same level of defect
detection (after inspection) can be achieved using
$(87-25)/87=71$\%less effort
\cite{tosun09}.

This is markedly
higher than other currently-used
industrial
methods such as manual code reviews. For example, 
A panel at {\em IEEE Metrics
2002}~\cite{shu02} concluded that manual software  reviews can find ${\approx}60\%$ 
of defects.
In other work, 
Raffo found that the defect detection capability of
industrial review methods have mode defect detection rates
of around 50\%
 for full Fagan inspections~\cite{fagan76} to
21\% for less-structured inspections.

Defect prediction scales well to a commercial
context. Defect predicting technology has been
commercialized in many tools including {\it Predictive}~\cite{turner06}, a
 product suite to analyze and predict
defects in software projects. Predictive was observed to
highlight simimilar issues to those found   with the more expensive tools. Significantly,
Predictive was able to faster process a larger code
base than the more expensive tool~\cite{turner06}.

### 2015-03-10 tuningpredictor.tex
Updates from ShareLaTeX

\documentclass{sig-alternative}
\usepackage{multirow}
\usepackage{color}
\usepackage{graphics}
\usepackage{rotating}
\usepackage{graphics}
\usepackage{colortbl} 
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%%% graph
\newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}
\newcommand{\rone}{\crule{1mm}{1.95mm}}
\newcommand{\rtwo}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
\newcommand{\rthree}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
\newcommand{\rfour}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}} 
\newcommand{\rfive}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
\newcommand{\quart}[3]{\begin{picture}(100,6)%1
{\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

@@

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Implications of Differential Evolution for  Defect Prediction:
Analytics Without Parameter Tuning Considered Harmful}
\numberofauthors{1}
\author{
\alignauthor
Wei Fu, Tim Menzies\\
       \affaddr{Computer Science, North Carolina State University, USA}\\
       {wfu@ncsu.edu, tim.menzies@gmail.com}}

\maketitle
\begin{abstract}
When learning
software defect predictors from static code attributes,   a
very simple optimizer called differential evolution needs can quickly
find  good tunings for that learner.
Such tunings can have a dramatic change to the performance of a learner;
e.g. in this paper we show that tuning can alter the precision of
a software defect predictor from 2\% to 98\%.

These results suggest that it is time to change standard practice in
software analytics. Specifically,
it is no longer enough to just run a data miner and present the result
{\em without} first conducting an tuning optimizations study.

@@

\vspace{1mm}
\noindent
{\bf Keywords:} defect prediction, CART, random forests,
Fastmap,   bootstrap sampling, effect size, A12.

@@

Many researchers have applied automatic optimizers to find good tunings.
This paper shows that for at least one software analytics problem
(software defect prediction from static code attributes),   a
very simple optimizer called differential evolution needs only   seconds
to just  few minutes to find good tunings.

These results   challenge much prior work into defect prediction:
\bi 
\item 
Several recent high profile papers have claimed 
that learnerX is better than learnerY for some software analytics task.
For example, a recent IEEE TSE article claimed that the 
CART decision tree learner was far worse than Random Forests for
softwre defect predition. 
We show that tuning can reverse the rankings of data miners such
that, after tuning, the worst untuned learner (CART) can out-perform the supposedly
best learner (Random Forests).
\item
The improvements achieved via differential evolution are too large to discount.
Yet those result show that different attributes are ``best'' for different
data sets and even differnt goals for the tunings. Hence, it is no longer
supportable to use data mining to argue that certain kinds of attributes
are better than others. 
\ei 
Given the simplicity and effectiveness of differential evolution,
and also given the effects this method has on defect prediction, this
paper  motivates  a change to the entire field of software analytics.
It is no longer enough to just run a data miner and present the result
{\em without} first conducting an tuning optimizations study.

@@

This section is our standard introduction to defect prediction~\cite{aa},
plus   some new results from Rahman et al.'s   2014 FSE paper~\cite{rahman14:icse}.

XXXX need our standard table

@@

\begin{figure*}[!t]
\renewcommand{\baselinestretch}{0.8}\begin{center}
{\scriptsize
\begin{tabular}{c|l|p{4in}}
amc & average method complexity & e.g. number of JAVA byte codes\\\hline
avg\_cc & average McCabe & average McCabe's cyclomatic complexity seen
in class\\\hline
ca & afferent couplings & how many other classes use the specific
class. \\\hline
cam & cohesion amongst classes & summation of number of different
types of method parameters in every method divided by a multiplication
of number of different method parameter types in whole class and
number of methods. \\\hline
cbm &coupling between methods &  total number of new/redefined methods
to which all the inherited methods are coupled\\\hline
cbo & coupling between objects & increased when the methods of one
class access services of another.\\\hline
ce & efferent couplings & how many other classes is used by the
specific class. \\\hline
dam & data access & ratio of the number of private (protected)
attributes to the total number of attributes\\\hline
dit & depth of inheritance tree &\\\hline
ic & inheritance coupling &  number of parent classes to which a given
class is coupled (includes counts of methods and variables inherited)
\\\hline
lcom & lack of cohesion in methods &number of pairs of methods that do
not share a reference to an instance variable.\\\hline
locm3 & another lack of cohesion measure & if $m,a$ are  the number of
$methods,attributes$
in a class number and $\mu(a)$  is the number of methods accessing an
attribute,\newline
then
$lcom3=((\frac{1}{a} \sum_j^a \mu(a_j)) - m)/ (1-m)$.
\\\hline
loc & lines of code &\\\hline
max\_cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
in class\\\hline
mfa & functional abstraction & number of methods inherited by a class
plus number of methods accessible by member methods of the
class\\\hline
moa &  aggregation &  count of the number of data declarations (class
fields) whose types are user defined classes\\\hline
noc &  number of children &\\\hline
npm & number of public methods & \\\hline
rfc & response for a class &number of  methods invoked in response to
a message to the object.\\\hline
wmc & weighted methods per class &\\\hline
\rowcolor{lightgray}
defect & defect & Boolean: where defects found in post-release bug-tracking systems.
\end{tabular}
}
\end{center}
\caption{OO measures used in our defect data sets. The last line shows
the dependent attribute (whether any defect is reported to  a
post-release bug-tracking system).}\label{fig:ck}
\end{figure*}

>>>>

\documentclass{sig-alternative}
\usepackage{multirow}
\usepackage{color}
\usepackage{graphics}
\usepackage{rotating}
\usepackage{graphics}
\usepackage{colortbl} 
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\footnotesize}{\scriptsize}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%%% graph
\newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}
\newcommand{\rone}{\crule{1mm}{1.95mm}}
\newcommand{\rtwo}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
\newcommand{\rthree}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
\newcommand{\rfour}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}} 
\newcommand{\rfive}{\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}\hspace{0.3pt}\crule{1mm}{1.95mm}}
\newcommand{\quart}[3]{\begin{picture}(100,6)%1
{\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}
\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

@@

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Implications of Differential Evolution for  Defect Prediction:
Analytics Without Parameter Tuning Considered Harmful?}
\numberofauthors{1}
\author{
\alignauthor
Wei Fu, Tim Menzies, Vivek Nair\\
       \affaddr{Computer Science, North Carolina State University, Raleigh, USA}\\
       {wfu@ncsu.edu, tim.menzies@gmail.com, vivekaxl@gmail.com}}

\maketitle
\begin{abstract}
When learning
software defect predictors,   a
very simple optimizer called differential evolution needs can quickly
find  good tunings for that learner.
Such tunings can have a dramatic change to the performance of a learner;
e.g. in this paper we show that tuning can alter the precision of
a software defect predictor from 2\% to 98\%.

These results prompt for a change to standard methods in software analytics.
At least for defect prediction, 
it is no longer enough to just run a data miner and present the result
{\em without} first conducting an tuning optimizations study.
The implications for other kinds of software analytics is now an open and pressing questions.

@@

\vspace{1mm}
\noindent
{\bf Keywords:} defect prediction, CART, random forests,
Fastmap,   bootstrap sampling, effect size, A12,differential evolution,
search-based software engineering.

@@

Many researchers have applied automatic optimizers to find good tunings.
This paper shows that for at least one software analytics problem
(software defect prediction from static code attributes),   a
very simple optimizer called differential evolution needs only   seconds
to just  few minutes to find good tunings.  
These results   challenge much prior work into defect prediction:
\bi 
\item 
Numerous   prominent papers have claimed 
that learnerX is better than learnerY for some software analytics task~\cite{lessmann2008benchmarking,hall11,me07b}.
For example, a recent IEEE TSE article claimed that the 
CART decision tree learner was far worse than Random Forests for
softwre defect predition~\cite{lessmann2008benchmarking}. 
Such conclusions do not survive tuning.
For example,
after tuning, the worst untuned learner (CART) can out-perform the supposedly
best learner (Random Forests).
\item
The improvements achieved via differential evolution are too large to discount.
Yet those result show that different attributes are ``best'' for different
data sets and even different goals for the tunings. Hence, it is no longer
supportable to use data mining to argue that certain kinds of attributes 
are better than others; e.g. as  done by~\cite{rahman2013how}. 
\ei 
Given the simplicity and effectiveness of differential evolution,
and also given the effects this method has on defect prediction, this
paper  motivates  a change to the entire field of software analytics.
At least for softwre defect prediction,
it is no longer enough to just run a data miner and present the result
{\em without} first conducting an tuning optimizations study.

The implications for other kinds of data mining tasks is unclear.
While this paper reports success with tuning defect predictors,
we were not so successful with
other analytics tasks (software development effort estimation).
Hence, we assert that it is now an open and pressing research question is whether or not  
tuning studies are now   required for research reports on software analytics.

@@

This section is our standard introduction to defect prediction~\cite{me15:book1},
plus   some new results from Rahman et al.'s   2014 FSE paper~\cite{rahman14:icse}.

\begin{figure*}[!t]
\renewcommand{\baselinestretch}{0.8}\begin{center}
{\scriptsize
\begin{tabular}{c|l|p{4in}}
amc & average method complexity & e.g. number of JAVA byte codes\\\hline
avg\_cc & average McCabe & average McCabe's cyclomatic complexity seen
in class\\\hline
ca & afferent couplings & how many other classes use the specific
class. \\\hline
cam & cohesion amongst classes & summation of number of different
types of method parameters in every method divided by a multiplication
of number of different method parameter types in whole class and
number of methods. \\\hline
cbm &coupling between methods &  total number of new/redefined methods
to which all the inherited methods are coupled\\\hline
cbo & coupling between objects & increased when the methods of one
class access services of another.\\\hline
ce & efferent couplings & how many other classes is used by the
specific class. \\\hline
dam & data access & ratio of the number of private (protected)
attributes to the total number of attributes\\\hline
dit & depth of inheritance tree &\\\hline
ic & inheritance coupling &  number of parent classes to which a given
class is coupled (includes counts of methods and variables inherited)
\\\hline
lcom & lack of cohesion in methods &number of pairs of methods that do
not share a reference to an instance variable.\\\hline
locm3 & another lack of cohesion measure & if $m,a$ are  the number of
$methods,attributes$
in a class number and $\mu(a)$  is the number of methods accessing an
attribute,\newline
then
$lcom3=((\frac{1}{a} \sum_j^a \mu(a_j)) - m)/ (1-m)$.
\\\hline
loc & lines of code &\\\hline
max\_cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
in class\\\hline
mfa & functional abstraction & number of methods inherited by a class
plus number of methods accessible by member methods of the
class\\\hline
moa &  aggregation &  count of the number of data declarations (class
fields) whose types are user defined classes\\\hline
noc &  number of children &\\\hline
npm & number of public methods & \\\hline
rfc & response for a class &number of  methods invoked in response to
a message to the object.\\\hline
wmc & weighted methods per class &\\\hline
\rowcolor{lightgray}
defect & defect & Boolean: where defects found in post-release bug-tracking systems.
\end{tabular}
}
\end{center}
\caption{OO measures used in our defect data sets.  Last line is
the dependent attribute (whether a defect is reported to  a
post-release bug-tracking system).}\label{fig:ck}
\end{figure*}

@@
